Implicit yaddayadda

### 2011-10-11 papers/PLDI2012/implicitization.tex
exemple

Now, see how our technique performs on this example.
Our combined technique gives us the expected invariant 
$\lstinline|x_old| \in~[-10000,10000]$.

\JH{Expliquer la figure 2}

\begin{figure}
\label{fig:multigraph}
\centering
\begin{minipage}[c]{.10\textwidth}
\begin{tikzpicture}[->,>=stealth',auto,node distance=2.1cm,
                    semithick,font=\footnotesize]

	\node[PRstate] (n00) {$p_0$};
	\node[PRstate] (n0) [below of=n00, yshift=0.8cm] {$p_1$};
	\node[PRstate] (n1) [below of=n0] {$p_2$};
	\node (label) [below of=n1, yshift=1.2cm] {Step 1};

@@

	\node[PRstate] (n00) {$p_0$};
	\node[PRstate] (n0) [below of=n00, yshift=0.8cm] {$p_1$};
	\node[PRstate] (n1) [below of=n0] {$p_2$};
	\node (label) [below of=n1, yshift=1.2cm] {Step 2};

>>>>

Now, see how our technique performs on this example.

Figure \ref{fig:example-graph} shows the sequence of subset of paths during the
analysis. The points in $P_R$ are noted $p_i$, where $i$ is the corresponding
line in the code: for instance, $p_5$ corresponds to the header of the main
loop.

\begin{enumerate}
	\item The first non-empty subset of paths is depicted on Figure
		\ref{fig:example-graph} Step 1. We apply Path-Focusing on this graph,
		and discover for $p_5$ the inductive invariant $\lstinline|x_old| = 0$.
		We also compute the set $P'$ of paths that have to be added at the next
		iteration. 
		For describing the different paths in the loop, we introduce the Boolean
		values $c_7, c_8, c_9$, where $c_i$ is \emph{true} when the path goes
		through the \emph{then} branch of the \emph{if-then-else} at line $i$, and
		\emph{false} when the path goes through the \emph{else} branch.
		We then add into $P'$ the following paths:
\JH{A compl\'eter}
\end{enumerate}

%Our combined technique gives us the expected invariant 
%$\lstinline|x_old| \in~[-10000,10000]$.

\begin{figure}
\label{fig:example-graph}
\centering
\begin{minipage}[c]{.10\textwidth}
\begin{tikzpicture}[->,>=stealth',auto,node distance=2.1cm,
                    semithick,font=\footnotesize]

	\node[PRstate] (n00) {$p_4$};
	\node[PRstate] (n0) [below of=n00, yshift=0.8cm] {$p_5$};
	\node[PRstate] (n1) [below of=n0] {$p_{11}$};
	\node (label) [below of=n1, yshift=1.2cm] {Step 1};

@@

	\node[PRstate] (n00) {$p_4$};
	\node[PRstate] (n0) [below of=n00, yshift=0.8cm] {$p_5$};
	\node[PRstate] (n1) [below of=n0] {$p_{11}$};
	\node (label) [below of=n1, yshift=1.2cm] {Step 2};
